### 2013-09-17 chi2014/introduction.tex

Our primary findings and contributions are as follows:
\begin{itemize}
\item The rates at which novel ideas and categories of ideas are produced follow logarithmic growth models, as a function of the total number of responses received, from all participants. In other words (and as one would expect), there are diminishing returns from asking more people to submit ideas. However, the actual rates differ per condition, as described below.
\item The rates for generating novel ideas are linked to the number of responses requested: The more responses requested from individuals, the higher the rate of novel idea generation, in general.
\item People are likely to come up with the same overall set of ideas early in their brainstorming process, but then diverge from this set of common ideas as they generate more ideas. Our data suggest that the first 20 ideas are the most unoriginal (i.e., the most common). This finding complements the previous finding, and further suggests that there is little value in requesting fewer than 20 ideas from workers.
\item Individuals' patterns of idea generation mimic those identified by Nijstaf and Stroebe's SIAM (search for ideas in associative memory) model \cite{nijstad_how_2006}: Workers produce a set of ideas from working memory, then switch strategies to generate ideas that are permutations of other ideas, a process we dub {\em riffing\/}. In our data, we see the prevalence of riffing steadily increase over the first 20 responses, after which its prevalence plateaus.
\item Requesting ``as many ideas as possible'' for a fixed price (fixed for the entire HIT, rather than per idea) is inadvisable, as it leads to a relatively low number of ideas produced (in our experiments, fewer than 20)
\end{itemize}

>>>>

Our primary findings and contributions are as follows:
\begin{itemize}
\item The rates at which novel ideas and categories of ideas are produced follow logarithmic growth models, as a function of the total number of responses received, from all participants. In other words (and as one would expect), there are diminishing returns from asking more people to submit ideas. However, the actual rates differ per condition, as described below
\item The rates for generating novel ideas are linked to the number of responses requested: The more responses requested from individuals, the higher the rate of novel idea generation, in general. [TODO: There is likely past work that has a similar finding; we should relate this finding to it. Taylor Berry Block as related? Diehl as related?]
\item People are likely to come up with the same overall set of ideas early in their brainstorming process, but then diverge from this set of common ideas as they generate more ideas. Our data suggest that the first 20 ideas are the most unoriginal (i.e., the most common). This finding complements the previous finding, and further suggests that there is little value in requesting fewer than 20 ideas from workers
\item Individuals' patterns of idea generation mimic those identified by Nijstaf and Stroebe's SIAM (search for ideas in associative memory) model \cite{nijstad_how_2006}: Workers produce a set of ideas from working memory, then switch strategies to generate ideas that are permutations of other ideas, a process we dub {\em riffing\/}. In our data, we see the prevalence of riffing steadily increase over the first 20 responses, after which its prevalence plateaus
\item Requesting ``as many ideas as possible'' for a fixed price (fixed for the entire HIT, rather than per idea) is inadvisable, as it leads to a relatively low number of ideas produced (in our experiments, fewer than 20)
\item The time spent producing an idea matches the times reported in previous studies \cite{nijstad_how_2006}
\end{itemize}

%Overall, across a number of metrics and perspectives (e.g., where novel ideas show up in the brainstorming process, time spent producing ideas), crowd brainstorming shares a number of similarities with brainstorming in more traditional environments.

### 2013-09-17 chi2014/related.tex

\section{Related Work}

% TODO Note: I plaigarized the wording on these definitions from wikipedia at this point, should pull from original Osborne at some point
Brainstorming was originally proposed in XXXX by Osborne [CITE]. Brainstorming makes several recommendations for idea generation in groups, the core of which are a set of four rules: \emph{focus on quantity}, \emph{withhold criticism}, \emph{welcome unusual ideas}, and \emph{combine and improve ideas}.

Since then, brainstorming as proposed by Osborne has been extensively evaluated. Very quickly, Taylor et. al established that \emph{nominal groups}, or individuals brainstorming in isolated whose ideas are later combined, performed better than real groups in terms of number of ideas generated [CITE]. Furthermore, Diehl and Stroebe found extremely high correlation (XX) between the number of ideas generated and the quality of ideas, a finding that has been verified many times since (Another citation here would be nice). In Bouchard and Hare [CITE], nominal brainstorming groups were able to generate quantities of ideas linear in the number of members in the group.

Electronic brainstorming is a variant in which individuals brainstorm at separate computer terminals, with the exchange of ideas performed over the network. Participants can enter ideas while simultaneously viewing the ideas of all other ideas, anonymously presented on-screen. Gallupe [CITE] found that electronic brainstorming reduced the inhibiting social effects of \emph{production blocking} (the inability for multiple people to speak at once), and \emph{evaluation apprehension} (the fear of judgment) in comparison to in-person groups. However, Pinsonneault et al identify four productivity impediments introduced by group electronic brainstorming, and show that there is little evidence to support the proposition that electronic brainstorming out-performs nominal brainstorming [CITE].

As crowd marketplaces do not tend to include built-in support for real-time communication between workers, nominal brainstorming groups provide the most reasonable assumption for providing a baseline assessment of performance. It is fortuitous, then, that prior work suggests that nominal groups are likely equivalent at worst to groups with the ability to communicate.

This choice is supported by other users of crowd marketplaces for idea generation. Yu and Nickerson use many individuals in an evolutionary algorithm to generate creative chair designs [CITE]. This technique is compared to single participants generating single ideas, but no baseline is established for idea generators individually exhausting a design space.

Something about another example. Maybe the Little iterative vs parallel paper? It includes creative tasks.

% TODO: part of this is Pao-exact, assuming it's cool because she's going to be an author on the paper
While there are no models of nominal brainstorming in the context of a crowd marketplace, several researchers have modelled the idea generation process for individuals and groups. We emphasize the former for its applicability to nominal groups. Nijstad and Stroebe define the \emph{search for ideas in associative memory} (SIAM) model. SIAM assumes two stages of idea generation: knowledge activation based on search of working memory, and idea production within a single activated image. This model verifies three predictions for individual brainstorming behaviour:

@@

Should we have another model here? I haven't read any yet.

>>>>

\section{Related Work}
In this section, we review related work in the areas of brainstorming and crowdsourcing.

% TODO Note: I plaigarized the wording on these definitions from wikipedia at this point, should pull from original Osborne at some point
In 1957, Osborne formalized the brainstorming process, providing a set of recommendations for idea generation by groups \cite{osborn_applied_1957}: \emph{focus on quantity}, \emph{withhold criticism}, \emph{welcome unusual ideas}, and \emph{combine and improve ideas}. These recommendations form the basis for the instructions we provide to workers in our experiments.

Following Osborne's work, Taylor et al.\ established that brainstorming by \emph{nominal groups}, or individuals working in isolation from one another, yields better results than collocated groups in terms of number of ideas generated \cite{taylor_does_1958}. These effects can be partially explained by the absence of counterproductive social forces, such as the fear of judgment. Bouchard and Hare \cite{bouchard_jr_size_1970}, later found that nominal brainstorming groups are able to generate quantities of ideas linear in the number of members in the group.

Electronic brainstorming is a variant in which individuals brainstorm at separate computer terminals, with the exchange of ideas performed over the network \cite{gallupe_electronic_1992}. Participants can enter ideas while simultaneously viewing the ideas of all other ideas, which are anonymously presented on-screen. As with nominal brainstorming, Gallupe \cite{gallupe_electronic_1992} observed that electronic brainstorming can reduce counterproductive social effects, such as production blocking (the inability for multiple people to speak at once) and fear of judgment, compared to physically collocated groups. However, Pinsonneault et al.\ \cite{pinsonneault_electronic_1999} identify productivity impediments introduced by group electronic brainstorming, such as being distracted by other ideas appearing, or individuals limiting their idea generation to avoid replicating the ideas of others. Given these drawbacks, their results suggest there is little evidence to support the proposition that electronic brainstorming outperforms nominal brainstorming.

Finally, Diehl and Stroebe found that groups that generate good ideas also generate \emph{many} ideas \cite{diehl_productivity_1987}, a finding that has been verified many times since [TODO: Need more backing refs here].

In terms of individual brainstorming processes, Nijstad and Stroebe provide a model for individual idea generation dubbed SIAM, or the search for ideas in associative memory. \cite{nijstad_how_2006}. SIAM defines two stages of idea generation: the generation of ideas based working memory, and idea production within a single activated ``image'' (where an image can be thought of as a category of ideas). This model predicts the following:

@@

Later, we will present evidence in support of this model from the data we collected.

In the realm of crowd-based brainstorming, there are a number of ways this process could be realized. The most basic configuration mirrors that of nominal brainstorming, where individuals brainstorm ideas in isolation of one another, and the resulting ideas are passed on to the requestor (the individual posting the brainstorming task). More sophisticated brainstorming environments are possible, such as those that provide awareness of ideas that others have generated, or those that rely on the crowd to organize or rank the ideas produced by others. In this paper, we focus on the most basic setup, where individuals brainstorm in isolation of one another.

While we are unaware of specific studies of brainstorming processes in crowd marketplaces, there is a range of related research examining more creative processes in this environment. For example, Yu and Nickerson created a system in which individuals participate in an evolutionary algorithm to generate creative chair designs \cite{yu_cooks_2011}. Compared to ideas produced by single individuals, they found the ideas produced as a result of their genetic algorithm were more creative. However, individuals produced only one idea each, compared to the many ideas typically produced by individuals in a brainstorming session. Thus, while their approach demonstrates the creative potential of the crowd, their results say little about brainstorming processes by crowds.

TODO: More crowdsourcing related work here. Maybe the Little iterative vs parallel paper? It includes creative tasks. Perhaps describe some of the unique characteristics of microtask marketplaces, like people's desire to perform a task and move on...
